A pipeline to analyse time-course gene expression data

### 2020-07-29 scripts/manuscript.Rmd

# Now use the results of the previous call to aheatmap to reorder the genes.
aheatmap(
    rescale_values(moanin_model[genes_to_plot,ord])[res$rowInd,],
    Colv=NA,
    Rowv=NA,
    annCol=orderedMeta[, c("Group", "Timepoint")],
    annLegend=TRUE,
    annColors=ann_colors,
    main=paste("Cluster", cluster_to_plot, "(rescaled)"),
    treeheight=0)

>>>>

# Now use the results of the previous call to aheatmap to reorder the genes.
aheatmap(
    rescale_values(moanin_model[genes_to_plot,ord])[res$rowInd,],
    Colv=NA,
    Rowv=NA,
    annCol=orderedMeta[, c("Group", "Timepoint")],
    annLegend=TRUE,
    annColors=ann_colors,
    main=paste("Cluster", cluster_to_plot, "(rescaled)"),
    treeheight=0)
```
